\texttt Lattice Based Key Exchange

### 2017-04-14 latex/keyexchange/secretkeybasedpublickeyencryption.tex
broke it!
that was fast!
improved randomize_public_key

\author{Ella Rose\inst{1}}
\institute{Paso Robles, CA \email{address@provider.com}}
\title[\texttt Design date]{\texttt Design date}

@@

\begin{abstract}
  We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas. The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple. Additionally, it is possible to utilize pre-existing RSA keypairs to perform the exchange. While doing so does not increase security beyond that of regular RSA, it is much faster.\\ 
\end{abstract}

@@

Then the value $c$ is shared with the owner of the public key. The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $p_1$ is an encryption of $0$, $p_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $p_2$. So when the decryption operation is applied, the result is $0 + 0 + e \equiv e$.

@@

\subsection{Re-using RSA keypairs for the exchange}
An RSA modulus can be used as a public key for the exchange presented previously; Simply substitute the RSA public key $n$ in place of the points $p_1$ and $p_2$, and modify the decryption algorithm to utilize a single modulo $p$ (as in the $p$ from $pq == n$). While this does not offer a security advantage to regular RSA encryption (here we offer no proof of security of any kind), it is significantly faster. Performing 1024 key exchanges using naive/textbook RSA-2048 requires approximately 1 second on our test machine; Performing 1024 key exchanges using the RSA-Lattice technique requires about .25 seconds on our test machine. This is largely the result of not needing to perform modular exponentiation with the lattice based technique.

\section{Conclusion}
 We define a simple lattice based key exchange algorithm. The algorithm utilizes 4 bignum multiplications and 4 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key. Public keys occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits. Interestingly, pre-existing RSA keypairs may be used to instantiate the shceme.
\end{document}

>>>>

\author{Ella Rose\inst{1}}
\institute{Paso Robles, CA \email{python_pride@protonmail.com}}
\title[\texttt Lattice Based Key Exchange]{\texttt Lattice Based Key Exchange}

@@

\begin{abstract}
  We define an algorithm for performing a key exchange between two parties utilizing lattice based ideas. The algorithm makes use of a small number of bignum multiplications and additions and is conceptually simple.\\ 
\end{abstract}

@@

Where $r_1$ and $r_2$ are randomly generated values of appropriate size.\todo{What sizes are appropriate?} Then the value $c$ is shared with the owner of the public key. The owner of the public key can recover $e$ by applying the homomorphic decryption operation of the secret key cipher to c; This is because $p_1$ is an encryption of $0$, $p_1 r_1$ is equivalent to $0 r_1 \equiv 0$, similar for $p_2$. So when the decryption operation is applied, the result is $0 + 0 + e \equiv e$.

@@

\section{Conclusion}
 We define a simple lattice based key exchange algorithm. The algorithm utilizes 4 bignum multiplications and 4 bignum additions to generate a keypair, 2 bignum multiplications and 2 bignum additions per key sent, and 2 modulo operations on bignums to receive a key. Public keys occupy < 1200 bits using current parameter cohices, while private keys require about 600 bits.
\end{document}
